Multi-fluids for Representing Sub-\change[HW]{filter}{grid}-scale Convection

### 2020-08-03 submit3/makeFigs/bubble.tex
Finished responding to Dan's comments

%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,british,times]{article}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[pdftex,a4paper]{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\pagestyle{empty}
\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear]{natbib}

@@

\includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}
\end{document}

>>>>

%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,british,times]{article}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[pdftex,a4paper]{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\pagestyle{empty}
\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear]{natbib}

@@

\includegraphics[width=0.75\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}\hspace{-0.2cm}\raisebox{0.5cm}{$\text{m}\text{s}^{-2}$}
\end{document}

### 2020-08-03 submit3/manuscript.tex
Finished responding to Dan's comments

\begin{table}
\begin{tabular}{l>{\raggedright}p{0.8\textwidth}}
$\sigma_{i}$ (-) & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$
\tabularnewline\hline
$\mathbf{u}$ ($\text{m}\text{s}^{-1}$)& 
Velocity of the single-fluid equations and velocity averaged over all fluids of the multi-fluid equations
\tabularnewline\hline
$\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$) & Velocity of fluid $i$ 
\tabularnewline\hline
$w_{i}$ ($\text{m}\text{s}^{-1})$& Vertical component of $\mathbf{u}_{i}$\tabularnewline\hline
$S_{ij}$ ($\text{s}^{-1}$)& Rate of volume fraction transfer from fluid $i$ to $j$ 
\tabularnewline\hline
$P$ ($\text{m}^{2}\text{s}^{-2}$)& \add[HW]{Boussinesq} pressure \add[HW]{potential} of the single-fluid equations $=p^{\prime}/\rho_{r}$  and pressure \add[HW]{potential} averaged over all fluids of the multi-fluid equations
\tabularnewline\hline
$P_i$ ($\text{m}^{2}\text{s}^{-2}$)& Pressure \add[HW]{potential} of fluid $i$
\tabularnewline\hline
$p_i$ ($\text{m}^{2}\text{s}^{-2}$)& $P_i - P$
\tabularnewline\hline
$\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$
\tabularnewline\hline
$b$ ($\text{m}\text{s}^{-2}$)& Buoyancy of single-fluid equations defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
where $\rho^{\prime}$ are departures in density from a horizontally
uniform reference, $\rho_{r}$  and buoyancy averaged over all fluids of the multi-fluid equations
\tabularnewline\hline
$b_{i}$ ($\text{m}\text{s}^{-2}$)& Buoyancy of fluid $i$ 
\tabularnewline\hline
$D_{i}\big/Dt$ ($\text{s}^{-1}$)& Total derivative with respect to fluid $i$ $=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$
\tabularnewline\hline
$\mathbf{D}_{ij}$ ($\text{m}\text{s}^{-2}$)& Drag on fluid $i$ from fluid $j$ 
\tabularnewline\hline
$\gamma$ ($\text{m}^{2}\text{s}^{-1}$)& Compressibility for calculating $p_i$ 
\tabularnewline\hline
$C_{D}$ (-)& Drag coefficient $=0$ or 1
\tabularnewline\hline
$r_{c}$ (m) & Plume radius used for defining the drag between fluids (m)\tabularnewline\hline
$\alpha$ ($\text{m}^{2}\text{s}^{-1}$)& Diffusivity of buoyancy 
\tabularnewline\hline
$\nu$ ($\text{m}^{2}\text{s}^{-1}$)& Viscosity 
\tabularnewline\hline
$\mathbf{k}$ (-)& Unit vector in the $z$-direction.
\tabularnewline
\end{tabular}
\caption{Definitions of variables (and units) for the single- and multi-fluid Boussinesq equations.\label{tab:defns}}
\end{table}

@@

To derive a transport equation for $\sigma_i$, (\ref{eq:LagrangianLabel}) is combined with $I_i$ times (\ref{eq:singleDivFree}) and volume averaged. 
It is necessary to assume that \change[DS]{operators permute}{partial derivatives commute} with the averaging \cite<as described by>{TWV+18}. \add[HW]{The equation for $\sigma_i$ is then}:
\begin{equation}
\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i}  =  \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\}
\label{eq:sigma}
\end{equation}
where $\sigma_{i}S_{ij}$ is the transfer rate from fluid $i$ to $j$ which must satisfy:
\begin{equation}
\sum_i \sum_{j\ne i} \bigl( \sigma_j S_{ji} - \sigma_i S_{ij} \bigr) =0.
\end{equation}
\add[DS]{These transfer terms account for the fact that the labels $I_i$ are not truly Lagrangian conserved (\ie\ fluid can transform from fluid $i$ to fluid $j$).}

Next the conditional averaging of terms in the momentum (\ref{eq:singleMom}) and buoyancy (\ref{eq:singleb}) equations is considered. \add[HW]{The filter scale is assumed to be equal to the grid scale but the derivation does not rely on this.} Conditionally averaging the advection terms leads to sub-filter-scale fluxes, $F_{SF}$, since the velocity and buoyancy are not uniform within each fluid at the filter scale:
\begin{eqnarray}
\nabla \cdot \overline{I_i \mathbf{u} \mathbf{u}} &=& \nabla \cdot (\sigma_i \mathbf{u}_i  \mathbf{u}_i) + F_\text{SF}^{\mathbf{u}_i} \\
\nabla \cdot \overline{I_i \mathbf{u} b} &=&  \nabla \cdot (\sigma_i \mathbf{u}_i b_i) + F_\text{SF}^{b_i}
\label{eq:filterAdvection}
\end{eqnarray}
The sub-filter-scale fluxes are represented by constant viscosity diffusion terms for each fluid. The diffusion terms are written so that, in the absence of transfers between fluids and if both fluids are initialized to be identical, the fluids remain identical and $\sigma_i$ acts as a passive tracer:
\begin{eqnarray}
\nu \nabla^2 \overline{I_i \mathbf{u}} &\approx& \sigma_i \nu \nabla^2 \mathbf{u}_i \\
\alpha \nabla^2 \overline{I_i b} &\approx& \sigma_i \alpha \nabla^2b_i .
\end{eqnarray} 
%
The \add[HW]{Boussinesq} pressure \add[HW]{potentials} within each fluid are defined as:
\begin{equation}
\sigma_i P_i = \overline{I_i P}.
\end{equation}
The pressure gradient can then be decomposed as:
\begin{equation}
\overline{I_i \nabla P} = \sigma_i \nabla P_i + 
    \left[ P_i\nabla\sigma_i - \overline{P\nabla I_i} \right]
\end{equation}
The terms in square brackets are the difference between the pressure force pushing outward from the fluid calculated using \change[HW]{resolved variables and the full resolved version}{the filtered variables and the fully resolved version} of the same force, both of which are related to drag. They will be represented by a drag, $\mathbf{D}_{ij}$. However this drag is likely to be smaller than the drag that is used, for example, in multi-phase modeling \cite<e.g.>{GBB+07} as it is representing the difference between two representations of drag, rather than the whole drag. Sensitivity to $\mathbf{D}_{ij}$ will be investigated in section \ref{sec:results}.

@@

\citeA{BN86} proposed a parameterization for pressure differences
in a multi-phase explosion model that has been widely used in mathematics
and engineering for simulating, for example, fluidized beds of granular material \cite<e.g.>{EHM92} and two compressible fluids \cite<e.g.>{SA99}. This model is not used here but is examined in order to derive a parameterization of pressure differences between fluids suitable for atmospheric convection.
\citeA{SA99} wrote transport equations for both the volume fraction,
$\sigma_{i}$, and for the mass fraction,
$\sigma_{i}\rho_{i}$, without transfers between fluids which in our notation are:
\begin{eqnarray}
\frac{\partial\sigma_{i}}{\partial t}+\mathbf{V}\cdot\nabla\sigma_{i} & = & \mu\left(P_{i}-P_{j}\right)
\label{eq:BNcompaction}
\\
\frac{\partial\sigma_{i}\rho_{i}}{\partial t}+\nabla\cdot\left(\sigma_{i}\rho_{i}\mathbf{u}_{i}\right) & = & 0
\label{eq:rhoTransport}
\end{eqnarray}
where $\mathbf{V}$ is the velocity of the interface between fluids,
$\mu$ is the compaction viscosity which controls how quickly the
pressure of each fluid relaxes to the mean pressure and index $j$
refers to the other fluid in a two fluid system.

@@

\citeA{TEB19} stabilized the multi-fluid equations by adding a diffusion
term $\nu\partial w^{2}/\partial z^{2}$ to the RHS of the $w$ equation.
If a fluid perturbation pressure is set to $p_i=-\nu\partial w/\partial z$
then this is equivalent to the diffusion term in one dimension. However adding an artificial diffusion term will harm three dimensional simulations of
resolved convection in the free troposphere whereas adding a fluid
perturbation pressure will not. Inspired by both \citeA{BN86} and
\citeA{TEB19}
and obeying the constraints given above, the pressure in each fluid is chosen to be:
\begin{equation}
p_{i}=
-\underbrace{\gamma\nabla\cdot\mathbf{u}_{i}}_{\text{stabilization}}
+
\underbrace{\gamma\sum_j \sigma_j\nabla\cdot\mathbf{u}_j}_{\text{correction}}
\label{eq:Pi_div}
\end{equation}
where $\gamma$ is a compressibility with units $\text{m}^2 \text{s}^{-1}$. The ``stabilization'' term reduces to that of \protect{\citeA{TEB19}} in one dimension and the ``correction'' term ensures that $\sum_i \sigma_i p_i =0$. It should be noted that this parameterization destroys \add[HW]{exact} energy conservation. \add[HW]{In future work solving the compressible equations, the energy lost due to this stabilization will be re-inserted as turbulent kinetic energy or heat.}

@@

Pressure differences between the fluids can lead to form drag which
is parameterized following \citeA{SW69}, \citeA{RC15} and \citeA{WM19} as: 
\begin{equation}
\mathbf{D}_{ij}=\frac{\sigma_{j}C_{D}}{r_{c}}|\mathbf{u}_{i}-\mathbf{u}_{j}|\left(\mathbf{u}_{i}-\mathbf{u}_{j}\right)\label{eq:dragBubble}
\end{equation}
where $C_{D}$ is a drag coefficient, $r_{c}$ is a cloud radius.
Sensitivity to $C_{D}/r_{c}$is explored in section \ref{sec:results}.

@@

Scale analysis can guide our choice of $\gamma$ for the parameterization of the pressure difference between fluids using the following assumptions:
\begin{enumerate}
\item The flow is buoyancy dominated.
\item The flow is close to inviscid.
\item The flow is slowly varying.
\item Fluid $i$ properties are anomalies from a neutrally stable resting
mean state 
implying that the average over all fluids of $b_i$, $\mathbf{u}_i$ and $P_i$ are zero.
\item Only the vertical direction is considered where $w_{ij}^{T}=0$.
\item $P_{i} = P + \gamma\sum_j \sigma_j\nabla\cdot\mathbf{u}_j 
                              - \gamma\nabla\cdot\mathbf{u}_{i}
             \approx-\gamma\nabla\cdot\mathbf{u}_{i}
            =-\gamma\frac{\partial w_{i}}{\partial z}$
\item $\frac{\partial \sigma_i}{\partial z} \approx 0$
\item There are two fluids 
\item Without loss of generality, the transfers $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
and $S_{ji}=0$ are used.
\item The drag term, $\mathbf{D}_{ij}$, is zero.
\end{enumerate}
These assumptions can be used to simplify the multi-fluid $w$ equation, ({\protect\ref{eq:mom})}:
\begin{equation}
\frac{\partial w_{i}^{2}}{\partial z}-\gamma\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
\end{equation}
This is non-dimensionalized using a length scale $L$, a buoyancy scale
$B$ and a time scale $T$ to get the non-dimensional variables:
\begin{eqnarray*}
\tilde{w} & = & w_{i}T/L\\
\tilde{b} & = & b_{i}/B\\
\tilde{z} & = & z/L
\end{eqnarray*}
The non-dimensional version of (\ref{eq:wi_balances}) is then:
\begin{equation}
\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilization}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
\end{equation}
The flow is buoyancy dominated so the buoyancy term should be $O(1)$
which implies the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$. Therefore, the non-dimensional momentum equation becomes:
\begin{equation}
\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilization}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
\end{equation}
The stabilization term must be large enough to smooth out oscillations
in $\tilde{w}$ due to advection and buoyancy but not too large to
remove all variability in $\tilde{w}$. Therefore the stabilization term should be $O(1)$ which implies that:
\begin{equation}
\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
\end{equation}
This will be used to guide the choice of $\gamma$ in section {\protect\ref{sec:results}}.

@@

Next \remove[HW]{eqn} (\ref{eq:b}) is solved for the buoyancy in each fluid, first
transporting buoyancy and then applying the transfer terms.
The advection term, $\mathbf{u}_i\nabla b_i$ is split into $\nabla\cdot(\mathbf{u}_i b_i) - b_i \nabla\cdot\mathbf{u}_i$ for better conservation as calculated by the finite volume method.
The transfer
terms can be very large due to the presence of $\frac{\sigma_{j}}{\sigma_{i}}S_{ij}$
in the transfer term for $b_{i}$ so they are treated operator split
and implicitly:
\begin{eqnarray}
b_{i}^{\prime} & = & b_{i}^{n}-\frac{\Delta t}{2}\Biggl(\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{n}\label{eq:transportb}\\
 &  & \hfill+\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{\ell}\Biggr)\\
b_{0}^{n+1} & = & b_{0}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{1}}{\sigma_{0}}\right)^{\prime\prime}S_{10}\left(b_{1}^{n+1}+b_{10}^{t}-b_{0}^{n+1}\right)-S_{01}b_{01}^{t}\right\} \label{eq:b0np1}\\
b_{1}^{n+1} & = & b_{1}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{0}}{\sigma_{1}}\right)^{\prime\prime}S_{01}\left(b_{0}^{n+1}+b_{01}^{t}-b_{1}^{n+1}\right)-S_{10}b_{10}^{t}\right\} \label{eq:b1np1}
\end{eqnarray}
where $b_{ij}^{t}=b_{ij}^{T}-b_{i}$. The use of $(\sigma_{0}/\sigma_{1})^{\prime\prime}$
from before the mass transfers is necessary to ensure bounded and
conservative transfers, as described by \cite{MWH20}. Simultaneous
solutions of (\ref{eq:b0np1}) and (\ref{eq:b1np1}) give:
\begin{eqnarray}
b_{0}^{n+1} & = & \frac{\left(1+T_{01}\right)\left(b_{0}^{\prime}-\Delta tS_{01}b_{01}^{t}+T_{10}b_{10}^{t}\right)+T_{10}\left(b_{1}^{\prime}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}\right)}{1+T_{01}+T_{10}}\\
b_{1}^{n+1} & = & \frac{b_{1}^{\prime}+T_{01}b_{0}^{n+1}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}}{1+T_{01}}
\end{eqnarray}
where $T_{ij}=\Delta t\left(\frac{\sigma_{i}}{\sigma_{j}}\right)^{\prime\prime}S_{ij}$

>>>>

\begin{table}
\begin{tabular}{l>{\raggedright}p{0.8\textwidth}}
$\sigma_{i}$ (-) & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$
\tabularnewline\hline
$\mathbf{u}$ ($\text{m}\text{s}^{-1}$)& 
Velocity of the single-fluid equations and velocity averaged over all fluids of the multi-fluid equations
\tabularnewline\hline
$\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$) & Velocity of fluid $i$ 
\tabularnewline\hline
$w_{i}$ ($\text{m}\text{s}^{-1})$& Vertical component of $\mathbf{u}_{i}$\tabularnewline\hline
$S_{ij}$ ($\text{s}^{-1}$)& Rate of volume fraction transfer from fluid $i$ to $j$ 
\tabularnewline\hline
$P$ ($\text{m}^{2}\text{s}^{-2}$)& \add[HW]{Boussinesq} pressure \add[HW]{potential} of the single-fluid equations $=p^{\prime}/\rho_{r}$  and pressure \add[HW]{potential} averaged over all fluids of the multi-fluid equations
\tabularnewline\hline
$P_i$ ($\text{m}^{2}\text{s}^{-2}$)& Pressure \add[HW]{potential} of fluid $i$
\tabularnewline\hline
$p_i$ ($\text{m}^{2}\text{s}^{-2}$)& $P_i - P$
\tabularnewline\hline
$\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$
\tabularnewline\hline
$b$ ($\text{m}\text{s}^{-2}$)& Buoyancy of single-fluid equations defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
where $\rho^{\prime}$ are departures in density from a horizontally
uniform reference, $\rho_{r}$  and buoyancy averaged over all fluids of the multi-fluid equations
\tabularnewline\hline
$b_{i}$ ($\text{m}\text{s}^{-2}$)& Buoyancy of fluid $i$ 
\tabularnewline\hline
$D_{i}\big/Dt$ ($\text{s}^{-1}$)& Total derivative with respect to fluid $i$ $=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$
\tabularnewline\hline
$\mathbf{D}_{ij}$ ($\text{m}\text{s}^{-2}$)& Drag on fluid $i$ from fluid $j$ 
\tabularnewline\hline
$\gamma$ ($\text{m}^{2}\text{s}^{-1}$)& \change[DS]{Compressibility}{Volume viscosity} for calculating $p_i$ 
\tabularnewline\hline
$C_{D}$ (-)& Drag coefficient $=0$ or 1
\tabularnewline\hline
$r_{c}$ (m) & Plume radius used for defining the drag between fluids (m)\tabularnewline\hline
$\alpha$ ($\text{m}^{2}\text{s}^{-1}$)& Diffusivity of buoyancy 
\tabularnewline\hline
$\nu$ ($\text{m}^{2}\text{s}^{-1}$)& Viscosity 
\tabularnewline\hline
$\mathbf{k}$ (-)& Unit vector in the $z$-direction.
\tabularnewline
\end{tabular}
\caption{Definitions of variables (and units) for the single- and multi-fluid Boussinesq equations.\label{tab:defns}}
\end{table}

@@

To derive a transport equation for $\sigma_i$, (\ref{eq:LagrangianLabel}) is combined with $I_i$ times (\ref{eq:singleDivFree}) and volume averaged. 
It is necessary to assume that \change[DS]{operators permute}{partial derivatives commute} with the averaging \cite<as described by>{TWV+18}. \add[HW]{The equation for $\sigma_i$ is then}:
\begin{equation}
\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i}  =  \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\}
\label{eq:sigma}
\end{equation}
where $\sigma_{i}S_{ij}$ is the transfer rate from fluid $i$ to $j$ which must satisfy:
\begin{equation}
\sum_i \sum_{j\ne i} \bigl( \sigma_j S_{ji} - \sigma_i S_{ij} \bigr) =0.
\end{equation}
\add[DS]{These transfer terms account for the fact that the labels $I_i$ are not truly Lagrangian conserved (i.e. fluid can transform from fluid $i$ to fluid $j$).}

Next the conditional averaging of terms in the momentum (\ref{eq:singleMom}) and buoyancy (\ref{eq:singleb}) equations is considered. \add[HW]{The filter scale is assumed to be equal to the grid scale but the derivation does not rely on this.} Conditionally averaging the advection terms leads to sub-filter-scale fluxes, $F_{SF}$, since the velocity and buoyancy are not uniform within each fluid at the filter scale:
\begin{eqnarray}
\nabla \cdot \overline{I_i \mathbf{u} \mathbf{u}} &=& \nabla \cdot (\sigma_i \mathbf{u}_i  \mathbf{u}_i) + F_\text{SF}^{\mathbf{u}_i} \\
\nabla \cdot \overline{I_i \mathbf{u} b} &=&  \nabla \cdot (\sigma_i \mathbf{u}_i b_i) + F_\text{SF}^{b_i}
\label{eq:filterAdvection}
\end{eqnarray}
The sub-filter-scale fluxes are represented by constant viscosity diffusion terms for each fluid. \add[DS]{Molecular diffusion is assumed to be of much smaller magnitude than this constant-viscosity turbulent diffusive mixing, so molecular diffusion is neglected hereafter.} The diffusion terms are written so that, in the absence of transfers between fluids and if both fluids are initialized to be identical, the fluids remain identical and $\sigma_i$ acts as a passive tracer:
\begin{eqnarray}
F_\text{SF}^{\mathbf{u}_i}
%\nu \nabla^2 \overline{I_i \mathbf{u}}
&\approx& \sigma_i \nu \nabla^2 \mathbf{u}_i \\
F_\text{SF}^{b_i}
%\alpha \nabla^2 \overline{I_i b}
&\approx& \sigma_i \alpha \nabla^2b_i .
\end{eqnarray} 
%
The \add[HW]{Boussinesq} pressure \add[HW]{potentials} within each fluid are defined as:
\begin{equation}
\sigma_i P_i = \overline{I_i P}.
\end{equation}
The pressure gradient can then be decomposed as:
\begin{equation}
\overline{I_i \nabla P} = \sigma_i \nabla P_i + 
    \left[ P_i\nabla\sigma_i - \overline{P\nabla I_i} \right]
\end{equation}
The terms in square brackets are the difference between the pressure force pushing outward from the fluid calculated using \change[HW]{resolved variables and the full resolved version}{the filtered variables and the fully resolved version} of the same force, both of which are related to drag. They will be represented by a drag, $\mathbf{D}_{ij}$. However this drag is likely to be smaller than the drag that is used, for example, in multi-phase modeling \cite<e.g.>{GBB+07} as it is representing the difference between two representations of drag, rather than the whole drag. Sensitivity to $\mathbf{D}_{ij}$ will be investigated in section \ref{sec:results}.

@@

\citeA{BN86} proposed a \remove[HW]{parameterization for pressure differences in a}
multi-phase explosion model that has been widely used in mathematics
and engineering for simulating, for example, fluidized beds of granular material \cite<e.g.>{EHM92} and two compressible fluids \cite<e.g.>{SA99}.
\add[HW]{This model has a separate pressure for each phase, $P_i$, and provides a transport equation for the phase fraction (equivalent of $\sigma_i$) which closes the system enabling diagnosis of $P_i$.}
This model is not used here but is examined in order to derive a parameterization of pressure differences between fluids suitable for atmospheric convection.
\citeA{SA99} wrote \add[HW]{the \protect\citeA{BN86} model using} transport equations for both the volume fraction, $\sigma_{i}$, and for the mass fraction,
$\sigma_{i}\rho_{i}$, without transfers between fluids which in our notation are:
\begin{eqnarray}
\frac{\partial\sigma_{i}}{\partial t}+\mathbf{V}\cdot\nabla\sigma_{i} & = & \mu\left(P_{i}-P_{j}\right)
\label{eq:BNcompaction}
\\
\frac{\partial\sigma_{i}\rho_{i}}{\partial t}+\nabla\cdot\left(\sigma_{i}\rho_{i}\mathbf{u}_{i}\right) & = & 0
\label{eq:rhoTransport}
\end{eqnarray}
where $\mathbf{V}$ is the velocity of the interface between fluids,
$\mu$ is the compaction viscosity which controls how quickly the
pressure of each fluid relaxes to the mean pressure and index $j$
refers to the other fluid in a two fluid system.

@@

\citeA{TEB19} stabilized the multi-fluid equations by adding a diffusion
term $\nu\partial w^{2}/\partial z^{2}$ to the RHS of the $w$ equation.
If a fluid perturbation pressure is set to $p_i=-\nu\partial w/\partial z$
then this is equivalent to the diffusion term in one dimension. However adding an artificial diffusion term will harm three dimensional simulations of
resolved convection in the free troposphere whereas adding a fluid
perturbation pressure will not. Inspired by both \citeA{BN86} and
\citeA{TEB19}
and obeying the constraints given above, the pressure in each fluid is chosen to be:
\begin{equation}
p_{i}=
-\underbrace{\gamma\nabla\cdot\mathbf{u}_{i}}_{\text{stabilization}}
+
\underbrace{\gamma\sum_j \sigma_j\nabla\cdot\mathbf{u}_j}_{\text{correction}}
\label{eq:Pi_div}
\end{equation}
where $\gamma$ is a \change[DS]{compressibility}{volume viscosity} with units $\text{m}^2 \text{s}^{-1}$. The ``stabilization'' term reduces to that of \protect{\citeA{TEB19}} in one dimension and the ``correction'' term ensures that $\sum_i \sigma_i p_i =0$. It should be noted that this parameterization destroys \add[HW]{exact} energy conservation. \add[HW]{In future work solving the compressible equations, the energy lost due to this stabilization will be re-inserted as turbulent kinetic energy or heat.}

@@

Pressure differences between the fluids can lead to form drag which
is parameterized following \citeA{SW69}, \citeA{RC15} and \citeA{WM19} as: 
\begin{equation}
\mathbf{D}_{ij}=\frac{\sigma_{j}C_{D}}{r_{c}}|\mathbf{u}_{i}-\mathbf{u}_{j}|\left(\mathbf{u}_{i}-\mathbf{u}_{j}\right)\label{eq:dragBubble}
\end{equation}
where $C_{D}$ is a drag coefficient and $r_{c}$ is a cloud radius.
Sensitivity to $C_{D}/r_{c}$is explored in section \ref{sec:results}.

@@

Scale analysis can guide our choice of $\gamma$ for the parameterization of the pressure difference between. \change[HW]{fluids using the following assumptions:}{The scaling presented can be derived using fewer assumptions than those below but these assumptions simplify the analysis:} 
\begin{enumerate}
\item The flow is buoyancy dominated.
\item The flow is close to inviscid.
\item The flow is slowly varying.
\item Fluid $i$ properties are anomalies from a neutrally stable resting
mean state 
implying that the average over all fluids of $b_i$, $\mathbf{u}_i$ and $P_i$ are zero.
\item Only the vertical direction is considered where $w_{ij}^{T}=0$.
\item $P_{i} = P + \gamma\sum_j \sigma_j\nabla\cdot\mathbf{u}_j 
                              - \gamma\nabla\cdot\mathbf{u}_{i}
             \approx-\gamma\nabla\cdot\mathbf{u}_{i}
            =-\gamma\frac{\partial w_{i}}{\partial z}$
\item $\frac{\partial \sigma_i}{\partial z} \approx 0$
\item There are two fluids 
\item Without loss of generality, the transfers $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
and $S_{ji}=0$ are used.
\item The drag term, $\mathbf{D}_{ij}$, is zero.
\end{enumerate}
These assumptions can be used to simplify the multi-fluid $w$ equation, ({\protect\ref{eq:mom})}:
\begin{equation}
\frac{\partial w_{i}^{2}}{\partial z}-\gamma\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
\end{equation}
This is non-dimensionalized using a length scale $L$, a buoyancy scale
$B$ and a time scale $T$ to get the non-dimensional variables:
\begin{eqnarray*}
\tilde{w} & = & w_{i}T/L\\
\tilde{b} & = & b_{i}/B\\
\tilde{z} & = & z/L
\end{eqnarray*}
The non-dimensional version of (\ref{eq:wi_balances}) is then:
\begin{equation}
\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilization}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
\end{equation}
The flow is buoyancy dominated so the buoyancy term should be $O(1)$
which implies the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$. Therefore, the non-dimensional momentum equation becomes:
\begin{equation}
\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilization}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
\end{equation}
The stabilization term must be large enough to smooth out oscillations
in $\tilde{w}$ due to advection and buoyancy but not too large to
remove all variability in $\tilde{w}$. Therefore the stabilization term should be $O(1)$ which implies that:
\begin{equation}
\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
\end{equation}
This will be used to guide the choice of $\gamma$ in section {\protect\ref{sec:results}}.

@@

Next \remove[HW]{eqn} (\ref{eq:b}) is solved for the buoyancy in each fluid, first
transporting buoyancy and then applying the transfer terms.
The advection term, $\mathbf{u}_i\cdot\nabla b_i$ is split into $\nabla\cdot(\mathbf{u}_i b_i) - b_i \nabla\cdot\mathbf{u}_i$ for better conservation as calculated by the finite volume method.
The transfer
terms can be very large due to the presence of $\frac{\sigma_{j}}{\sigma_{i}}S_{ij}$
in the transfer term for $b_{i}$ so they are treated operator split
and implicitly:
\begin{eqnarray}
b_{i}^{\prime} & = & b_{i}^{n}-\frac{\Delta t}{2}\Biggl(\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{n}\label{eq:transportb}\\
 &  & \hfill+\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{\ell}\Biggr)\\
b_{0}^{n+1} & = & b_{0}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{1}}{\sigma_{0}}\right)^{\prime\prime}S_{10}\left(b_{1}^{n+1}+b_{10}^{t}-b_{0}^{n+1}\right)-S_{01}b_{01}^{t}\right\} \label{eq:b0np1}\\
b_{1}^{n+1} & = & b_{1}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{0}}{\sigma_{1}}\right)^{\prime\prime}S_{01}\left(b_{0}^{n+1}+b_{01}^{t}-b_{1}^{n+1}\right)-S_{10}b_{10}^{t}\right\} \label{eq:b1np1}
\end{eqnarray}
where $b_{ij}^{t}=b_{ij}^{T}-b_{i}$. The use of $(\sigma_{0}/\sigma_{1})^{\prime\prime}$
from before the mass transfers is necessary to ensure bounded and
conservative transfers, as described by \cite{MWH20}. Simultaneous
solutions of (\ref{eq:b0np1}) and (\ref{eq:b1np1}) give:
\begin{eqnarray}
b_{0}^{n+1} & = & \frac{\left(1+T_{01}\right)\left(b_{0}^{\prime}-\Delta tS_{01}b_{01}^{t}+T_{10}b_{10}^{t}\right)+T_{10}\left(b_{1}^{\prime}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}\right)}{1+T_{01}+T_{10}}\\
b_{1}^{n+1} & = & \frac{b_{1}^{\prime}+T_{01}b_{0}^{n+1}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}}{1+T_{01}}
\end{eqnarray}
where $T_{ij}=\Delta t\left(\frac{\sigma_{i}}{\sigma_{j}}\right)^{\prime\prime}S_{ij}$
